Postural developments modulate children's visual access to social information

### 2018-05-11 writeup-cogsci/cogsci2018_cameraReady.Rmd
cut a few last words, references, and rearranged

```
# Introduction
From early infancy, children are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

@@

We created a situation in the lab in which the context of interaction was tightly controlled, but as children grow and change, the activities in which they engage with their caregivers also vary, leading to differences in the distribution of contexts they experience. Thus, more work is needed to understand how our results relate to children's home experiences [@fausey2016]. The ability to walk is part of a cascade of changes in children's  experience, and our study captures only a cross-sectional slice of this broader, multifaceted trajectory.

>>>>

```
# Introduction
From early infancy, children are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring].

@@

We created a situation in which the context of interaction was tightly controlled, but as children grow and change, the activities in which they engage with their caregivers also vary, leading to differences in the distribution of contexts they experience. Thus, more work is needed to understand how our results relate to children's home experiences [@fausey2016]. The ability to walk is part of a cascade of changes in children's  experience, and our study captures only a cross-sectional slice of this broader, multifaceted trajectory.

### 2018-05-11 writeup-cogsci/cogsci2018_cameraReady.tex
cut a few last words, references, and rearranged

From early infancy, children are deeply engaged in learning from others.
Even newborns tend to prefer to look at faces with direct vs.~averted
gaze (Farroni, Csibra, Simion, \& Johnson, 2002) and young infants
follow overt gaze shifts (Gredeb\wrapmf{\"{a}}ck, Fikke, \& Melinder,
2010). Further, when infants attend to video stimuli, they tend to look
mostly at faces at the expense of other visual information -- though
older infants start to look towards people's hands and the actions they
are performing (Frank, Amso, \& Johnson, 2014; Frank, Vul, \& Saxe,
2012).

@@

We created a situation in the lab in which the context of interaction
was tightly controlled, but as children grow and change, the activities
in which they engage with their caregivers also vary, leading to
differences in the distribution of contexts they experience. Thus, more
work is needed to understand how our results relate to children's home
experiences (Fausey et al., 2016). The ability to walk is part of a
cascade of changes in children's experience, and our study captures only
a cross-sectional slice of this broader, multifaceted trajectory.

@@

\hypertarget{ref-frank2014visual}{}
Frank, M. C., Amso, D., \& Johnson, S. P. (2014). Visual search and
attention to faces during early infancy. \emph{Journal of Experimental
Child Psychology}, \emph{118}, 13--26.

>>>>

From early infancy, children are deeply engaged in learning from others.
Even newborns tend to prefer to look at faces with direct vs.~averted
gaze (Farroni, Csibra, Simion, \& Johnson, 2002) and young infants
follow overt gaze shifts (Gredeb\wrapmf{\"{a}}ck, Fikke, \& Melinder,
2010). Further, when infants attend to video stimuli, they tend to look
mostly at faces at the expense of other visual information -- though
older infants start to look towards people's hands and the actions they
are performing (Frank, Vul, \& Saxe, 2012).

@@

We created a situation in which the context of interaction was tightly
controlled, but as children grow and change, the activities in which
they engage with their caregivers also vary, leading to differences in
the distribution of contexts they experience. Thus, more work is needed
to understand how our results relate to children's home experiences
(Fausey et al., 2016). The ability to walk is part of a cascade of
changes in children's experience, and our study captures only a
cross-sectional slice of this broader, multifaceted trajectory.

@@
